---
title: "iteration and listcols"
author:  "Alexey Abramov"
date: "11/9/2020"
output: 
  github_document:
    toc: true
---

# Setup

```{r, setup}
library(tidyverse)
library(rvest)


knitr::opts_chunk$set(
  fig.width = 6,
  fig.height = 6,
  out.width = "90%"
)

theme_set(
  ggthemes::theme_fivethirtyeight() + theme(legend.position = "bottom")
  )

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.colour = "viridis"
)

scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

# Lists

You can put anything in a list...

```{r}
l = list(
  vec_number = 5:8,
  vec_logical = c(TRUE, TRUE, FALSE, TRUE, FALSE, FALSE),
  mat = matrix(1:8, nrow = 2, ncol = 4),
  summary = summary(rnorm(100)))
```

```{r}
l
l$vec_number
l[[1]]
l[["vec_number"]]
mean(l[[1]])

```

## for loops

```{r}
list_norm = 
  list(
    a = rnorm(20, 3, 1),
    b = rnorm(20, 2, 5),
    c = rnorm(20, -4, 2),
    d = rnorm(20, 5, 2))
```

Pause and get my old function...

```{r}
mean_and_sd = function(x) {
  
  if (!is.numeric(x)) {
    stop("Input must be numeric")
  }
  
  if (length(x) < 3) {
    stop("Input must have at least three numbers")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)
  
  tibble(
    mean = mean_x,
    sd = sd_x
  )
  
}
```


```{r}
mean_and_sd(list_norm[[1]])
mean_and_sd(list_norm[[2]])
mean_and_sd(list_norm[[3]])
mean_and_sd(list_norm[[4]])
```

Ok, so let's use a for loop
```{r}
output = vector("list", length = 4)
```

```{r}
output[[1]] = mean_and_sd(list_norm[[1]])

for (i in 1:4) {
  
  output[[i]] = mean_and_sd(list_norm[[i]])
  
}
```

Let's try map.

```{r}
map(list_norm, mean_and_sd)
```

Ok, what about another function!
Just put it in the second argument.

```{r}
output1 = map(list_norm, median)
output2 = map(list_norm, IQR)
```

If we just want numbers... we'll get a vector.

```{r}
output3 = map_dbl(list_norm, median)
```

Or a dataframe

```{r}
output4 = map_df(list_norm, mean_and_sd, .id = "input")
```

List columns so you don't have to keep track of all these different outputs

```{r}
list_df = 
  tibble(
    name = c("a", "b", "c", "d"),
    samp = list_norm
  )

list_df %>% 
  filter(name == "a")
```

Ok , let's map a dataframe!

```{r}
map(list_df$samp, mean_and_sd)
```

Alright but we want this output to be back in the dataframe

```{r}
list_df =
  list_df %>% 
  mutate(
    summary = map_df(samp, mean_and_sd),
    medians = map_dbl(samp, median))
```

